Formalizing Stack Safety as a Security Property

### 2021-12-21 submission4/main.tex
Last submission

@@

%\author{
%  \IEEEauthorblockN{
%    Sean Noble Anderson
%  }
%  \IEEEauthorblockA{
%    Portland State University\\
%    ander28@pdx.edu
%  }
%  \and
%  \IEEEauthorblockN{
%    Leonidas Lampropoulos,
%  }
%  \IEEEauthorblockA{
%    University of Maryland, College Park\\
%    leonidas@umd.edu
%  }
%  \and
%  \IEEEauthorblockN{
%    Roberto Blanco,
%  }
%  \IEEEauthorblockA{
%    Max Planck Institute for Security and Privacy\\
%    roberto.blanco@mpi-sp.org
%  }
%  \and
%  \IEEEauthorblockN{
%    Benjamin C. Pierce,
%  }
%  \IEEEauthorblockA{
%    University of Pennsylvania\\
%    bcpierce@cis.upenn.edu
%  }
%  \and
%  \IEEEauthorblockN{
%    Andrew Tolmach
%  }
%  \IEEEauthorblockA{
%    Portland State University\\
%    tolmach@pdx.edu
%  }
%}

>>>>

\makeatletter
\newcommand{\linebreakand}{%
  \end{@IEEEauthorhalign}
  \hfill\mbox{}\par
  \mbox{}\hfill\begin{@IEEEauthorhalign}
}
\makeatother

@@

\author{
  \IEEEauthorblockN{
    Sean Noble Anderson
  }
  \IEEEauthorblockA{
    Portland State University\\
    ander28@pdx.edu\\
  }
  \and
  \IEEEauthorblockN{
    Leonidas Lampropoulos
  }
  \IEEEauthorblockA{
    University of Maryland, College Park\\
    leonidas@umd.edu\\
  }
  \and
  \IEEEauthorblockN{
    Roberto Blanco
  }
  \IEEEauthorblockA{
    Max Planck Institute for Security and Privacy\\
    roberto.blanco@mpi-sp.org\\
  }
  \linebreakand
  \IEEEauthorblockN{
    Benjamin C. Pierce,
  }
  \IEEEauthorblockA{
    University of Pennsylvania\\
    bcpierce@cis.upenn.edu\\
  }
  \and
  \IEEEauthorblockN{
    Andrew Tolmach
  }
  \IEEEauthorblockA{
    Portland State University\\
    tolmach@pdx.edu\\
  }
}
